\documentclass{beamer}

% usepackage
\usepackage{url}

% Theme choice:
\usetheme{Madrid}


% Title page details: 
\title{\textit{A Journey of Submission and Revision}}
% \subtitle{A Personal Perspective}
\author[xjh]{Jiahao Xiang\inst{1}}
\institute{
    \inst{1}
    Hengyang Normal University
}
\date{\today}

\begin{document}




% Title page frame
\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{\textit{TimeLine}}
    \begin{itemize}
        \item Submitted - Jan 09, 2024
        \item With Editor - Jan 10, 2024
        \item Under Review - Jan 17, 2024
        \item Revise - Feb 07, 2024
        \item Revise Approval - Feb 20, 2024
        \item Under Review - Feb 28, 2024
        \item Decision in Process - Mar 05, 2024
        \item Revise - Mar 07, 2024
        \item Accept - Mar 08, 2024
        \item Proofs available for checking - Mar 14, 2024
        \item Final version of your article published online - Mar 15, 2024
    \end{itemize}
\end{frame}

% Outline frame
% \begin{frame}{Content}
%     \tableofcontents
% \end{frame}
\AtBeginSection[ ]
{
    \begin{frame}{\textit{Content}}
        \tableofcontents[currentsection]
    \end{frame}
}

% main content

\section{Preparation}

\begin{frame}{\textit{Finding a Suitable Set of Journals}}
    \textbf{Methods:}
    \begin{enumerate}
        \item \textbf{Keyword Search}
              \begin{itemize}
                  \item Use \textit{Google Scholar} to search for papers with similar keywords and note the journals they're published in.
              \end{itemize}
        \item \textbf{Journal Recommendation Systems}
              \begin{itemize}
                  \item Use \textit{Journal Finder of Elsevier}\footnote{\url{https://journalfinder.elsevier.com/}} or \textit{Journal Search of Springer}\footnote{\url{https://link.springer.com/search?facet-content-type="Journal"}} to find suitable journals based on your paper's topic and scope.
              \end{itemize}
    \end{enumerate}
\end{frame}


\begin{frame}{\textit{Selecting the Appropriate Journal}}
    \textbf{Filter conditions:}
    \begin{enumerate}
        \item \textbf{Journal's Level}
              \begin{itemize}
                  \item Quartiles: Q1, Q2, Q3, Q4
                  \item CCF Ranking: A, B, C
              \end{itemize}
        \item \textbf{Journal's Scope}
              \begin{itemize}
                  \item Journal's website: Check the scope
                  \item Submission system: Check "Select Submission Classifications", more accurate
                  \item Latest papers: Check the latest papers, find the most related ones
              \end{itemize}
        \item \textbf{Journal's Review Time}
              \begin{itemize}
                  \item Average review time: Find the newest issue, check the review time of the latest papers
                  \item Experience posts: Find posts about the journal, like on the \textit{Letpub} website
              \end{itemize}

    \end{enumerate}
\end{frame}

\section{Submission}

\begin{frame}{\textit{Guide for Authors}}
    \begin{enumerate}
        \item \textbf{Submission Checklist:} Ensure all materials are prepared
              \begin{itemize}
                  \item Cover Letter
                  \item Manuscript
                  \item Declaration of Interest: Use the tool provided by Elsevier\footnote{\url{https://declarations.elsevier.com/home}} to create this.
              \end{itemize}
        \item \textbf{Typesetting:} Follow the journal's typesetting requirements
              \begin{itemize}
                  \item Word Document: Typeset according to the journal's requirements or use the template provided by the journal.
                  \item \LaTeX: Use a common template like the one provided by Elsevier\footnote{\url{https://www.elsevier.com/researcher/author/policies-and-guidelines/latex-instructions}}.
              \end{itemize}
    \end{enumerate}
\end{frame}

\begin{frame}{\textit{Using Editorial Manager for Submissions}}
    \begin{enumerate}
        \item \textbf{Tutorial:} A tutorial for using Editorial Manager (EM) as an author is available on Bilibili\footnote{\url{https://www.bilibili.com/video/BV1yz4y1W7B9/}}.
        \item \textbf{Tips:}
              \begin{itemize}
                  \item Be aware of specific files that need to be updated, such as the Highlight.
                  \item If you change your Corresponding Author, the submission will be transferred to the new Corresponding Author's account. You will no longer be able to see the submission in your original account.
              \end{itemize}
    \end{enumerate}
\end{frame}

\section{Revision}

\begin{frame}{\textit{Revision is Half the Battle Towards Acceptance}}
    \textbf{Key Tips:}
    \begin{itemize}
        \item \textit{Respect Reviewers:} Value the reviewers' opinions and implement necessary changes.
        \item \textit{Rebut Thoughtfully:} If you disagree with the reviewers' opinions, provide a well-reasoned rebuttal.
        \item \textit{Address All Comments:} Ensure all comments from reviewers are thoroughly addressed.
    \end{itemize}
\end{frame}


\begin{frame}{\textit{Thank You}}
    \centering
    \Large
    Thank you for your attention! \\
    \normalsize
    The Slide is available on GitHub{\footnotesize\footnote{\url{https://raw.githubusercontent.com/jiahaoxiang2000/TempWrite/master/slied/submission.pdf}}}.
\end{frame}

\end{document}